Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-26 thesis/thesis.tex
thesis: Sort key words

{\bf Key words.} open clusters characterization, machine learning, gaia, data analysis, deep embedded clustering

@@

{\bf Palabras Clave:} caracterización de cúmulos abiertos, inteligencia artificial, gaia, análisis de datos

>>>>

{\bf Key words.} data analysis, deep embedded clustering, gaia, machine learning, open clusters characterization

@@

{\bf Palabras Clave:} análisis de datos, caracterización de cúmulos abiertos, gaia, inteligencia artificial
